### 2021-06-25 chapters/3_background.tex
changed neural net to machine learning model

\section{Clustering algorithms}
This research focuses on clustering mutants and use of existing clustering algorithms. 
Many different types of clustering algorithms have been proposed\cite{Rodriguez2019}. While there is a lot of diversity, some methods are more frequently used than others\cite{Wu2008TopMining}. 
Rodriguez et al., compared the performance of nine different clustering algorithms:
\begin{itemize}
    \item k-means
    \item CLARA
    \item hierarchical
    \item EM
    \item hcmodel
    \item spectral
    \item subscpace
    \item optics
    \item dbscan
\end{itemize}
The goal of their study was to guide researchers, who have little experience in data mining techniques, to the application of clustering methods.
They evaluated the algorithms in three distinct situations: default parameters, single parameter variation and random variation of parameters.
They used 400 generated artificial data sets which were normally distributed.
\newline
The results reported in their research are respective to specific configurations of normally distributed data and algorithmic implementations.
Nonetheless they do give a good overview on how the algorithms compare to each other.
\newline
For the default parameter situation the spectral clustering algorithm had the best performance and the hierarchical algorithm had the worst performance.
\newline
Regarding single parameter variations, for data sets containing 2 columns, the hierarchical, optics and EM methods showed significant performance variation.
\newline
With respect to the multidimensional analysis for data sets, the performance of the algorithms for the multidimensional selection of parameters was similar to that using the default parameters.
They conclude their research with observing that, for data sets with 10 or more columns the spectral algorithm consistently provided the best performance.
However the EM, hierarchical, k- means and subspace algorithms can also achieve similar performance with some parameter tuning.
The optics and dbscan algorithms aim at different data distributions than performed in this study. There different results could be obtained for non-normally distributed data.
\end{document}

>>>>

\section{Clustering algorithms}
This research focuses on clustering mutants and use of existing clustering algorithms. 
Many different types of clustering algorithms have been proposed\cite{Rodriguez2019}. While there is a lot of diversity, some methods are more frequently used than others\cite{Wu2008TopMining}. 
Rodriguez et al., compared the performance of nine different clustering algorithms:
\begin{itemize}
    \item k-means
    \item CLARA
    \item hierarchical
    \item EM
    \item hcmodel
    \item spectral
    \item subscpace
    \item optics
    \item dbscan
\end{itemize}
The goal of their study was to guide researchers, who have little experience in data mining techniques, to the application of clustering methods.
They evaluated the algorithms in three distinct situations: default parameters, single parameter variation and random variation of parameters.
They used 400 generated artificial data sets which were normally distributed.
\newline
The results reported in their research are respective to specific configurations of normally distributed data and algorithmic implementations.
Nonetheless they do give a good overview on how the algorithms compare to each other.
\newline
For the default parameter situation the spectral clustering algorithm had the best performance and the hierarchical algorithm had the worst performance.
\newline
Regarding single parameter variations, for data sets containing 2 columns, the hierarchical, optics and EM methods showed significant performance variation.
\newline
With respect to the multidimensional analysis for data sets, the performance of the algorithms for the multidimensional selection of parameters was similar to that using the default parameters.
They conclude their research with observing that, for data sets with 10 or more columns the spectral algorithm consistently provided the best performance.
However the EM, hierarchical, k- means and subspace algorithms can also achieve similar performance with some parameter tuning.
The optics and dbscan algorithms aim at different data distributions than performed in this study. There different results could be obtained for non-normally distributed data.

\section{Machine learning models for clustering}
\label{ch:neuralNetworkSurvey}
There are many different types of machine learning models.
These models have different applications based on their properties.
For this thesis we will focus on machine learning models designed for clustering.
\newline
Machine learning algorithms are divided in supervised and unsupervised learning algorithms\cite{supervisedUnsupervised}.
Supervised machine learning algorithms are commonly used for classification and categorization\cite{supervisedUnsupervised}.
Unsupervised machine learning algorithms are commonly used for clustering and dimensionality reduction\cite{supervisedUnsupervised}.
\newline
K.L. Du surveyed different machine learning algorithms used for clustering\cite{Du2010Clustering:Approach}:
\begin{itemize}
    \item Self organizing map.
    \item Learning vector quantization.
    \item C-means clustering.
    \item Mountain clustering.
    \item Neural gas.
    \item ART networks.
    \item Fuzzy c-means.
\end{itemize}
In his paper he also touches on subjects relevant to clustering and machine learning models such as the under-utilization problem, fuzzy clustering, robust clustering, clustering based on non- Euclidean distance measures, supervised clustering, and hierarchical clustering.
Machine learning model variants and their references are also discussed.
\newline
K.L. Du describes the mathematical principles on which the machine learning algorithms are based.
He closes his paper with computer simulations of some of the machine learning models he surveyed.

\end{document}

### 2021-06-25 chapters/rq2/1_experiment_design.tex
changed neural net to machine learning model

\documentclass[../../main]{subfiles}
\begin{document}
% Because we use sections but these sections should be interpreted as chapters for rq1 and rq2 sectioning.
\clearpage
\section{Experiment design}
In this chapter we will design an experiment to answer our second research question.
HYOPTHESIS HERE\todo{do hypothesis}
Our goal is to achieve a mutation score that is as close as possible to the mutation score of a full set of executed mutants.
\newline
\todo{finish this}

\subsection{Selecting a neural network}
Our starting point for selecting a neural network is the survey done by K.L. Du\cite{Du2010Clustering:Approach}.
We start with a process of elimination to filter the neural networks named in chapter \ref{ch:background}.
\newline
supervised networkd\todo{elaborate why no supervised}
\newline
The moutain clustering networks is effective method for estimating the number of clusters\cite{Du2010Clustering:Approach}. 
The goal of this experiment is to cluster mutants, while finding out the number of clusters we need might be valuable it is not what we want to achieve. Therefore we will not select mountain clustering.
Subtractive clustering is a modified form of mountain c\cite{Du2010Clustering:Approach}. 
\newline

>>>>

\documentclass[../../main]{subfiles}
\begin{document}
% Because we use sections but these sections should be interpreted as chapters for rq1 and rq2 sectioning.
\clearpage
\section{Experiment design}
In this chapter we will design an experiment to answer our second research question.
We hypothesise that we train a machine learning model with the set of characteristics we identified
while maintaining effectiveness and reducing the amount executed when executing one mutant from each cluster that is randomly selected.
Our goal is to achieve a mutation score that is as close as possible to the mutation score of a full set of executed mutants.
\newline
\todo{finish this}

\subsection{Selecting a machine learning model}
Our starting point for selecting a machine learning model is the survey done by K.L. Du\cite{Du2010Clustering:Approach}.
We start with a process of elimination to filter the machine learning models named in chapter \ref{ch:background}.
\newline
supervised learning\todo{elaborate why no supervised}
\newline
The moutain clustering model is effective method for estimating the number of clusters\cite{Du2010Clustering:Approach}. 
The goal of this experiment is to cluster mutants, while finding out the number of clusters we need might be valuable it is not what we want to achieve. Therefore we will not select mountain clustering.
Subtractive clustering is a modified form of mountain c\cite{Du2010Clustering:Approach}. 
\newline
